---
title: "Analysis"
author: "JS"
date: "22/03/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Load the tidyverse:
```{r}
library(tidyverse)
```
Read in the data:
```{r}
dat <- read_csv("data/raw/2017_super-rugby_try-source-data.csv")
```
Check for missing values and their locations:
```{r}
sum(is.na(dat))
```
```{r}
naniar::vis_miss(dat)
```
Create exploratory graphs to visualise the univariate distribution (i.e. variation in single variables) for the following variables: attacking_team, game_time, try_source, final_source, possession_zone, time_from_source:
```{r}
ggplot(data = dat) +
  geom_bar(mapping = aes(x = attacking_team), colour = "black", fill = "chartreuse")
```
```{r}
ggplot(data = dat) +
  geom_histogram(mapping = aes(x = game_time), bins = 20, colour = "magenta")
```
```{r}
ggplot(data = dat) +
  geom_bar(mapping = aes(x = try_source), fill = "dodgerblue")
```
```{r}
ggplot(data = dat) +
  geom_bar(mapping = aes(x = final_source), fill = "magenta")
```
```{r}
ggplot(data = dat) +
  geom_histogram(mapping = aes(x = time_from_source), bins = 20)
```
```{r}
ggplot(data = dat) +
  geom_bar(mapping = aes(x = possession_zone), colour = "green")
```
Create charts exploring 2 variables at once:
```{r}
ggplot(data = dat) +
geom_point(mapping = aes(x = game_time, y = time_from_source, shape = try_source)) +
  facet_wrap(~ possession_zone, nrow = 2)
```
Create some summary stats of continuos variables:
```{r}
summary <- dat %>%
  group_by(attacking_rank) %>%
  summarise_at(vars("time_from_source", "total_passes"), mean)
```

```{r}
ggplot(data = summary) +
  geom_col(mapping = aes(x = attacking_rank, y = total_passes))
```

